An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-04 poly-embed-journal/poly-embed-journal.tex
Comments on Section 5

%% overview of the applications
Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete target loss, as well as to verify consistency or inconsistency for specific surrogate and link pairs.
Below, we illustrate the power of this framework with specific examples from the literature.
To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function and surrogate regret bounds (\S~\ref{sec:abstain}). \jessiet{regret bounds?}
We then give three examples of subsequent works that use our framework, in the context of structured binary classification (\S~\ref{sec:lovasz-hinge}), multiclass classification (\S~\ref{sec:winge}), and top-$k$ classification (\S~\ref{sec:top-k}).
In all cases, our framework illuminates the behavior of inconsistent surrogates by revealing the discrete losses they embed, i.e., the true targets for which they are consistent.
In structured binary classification and top-$k$ classification, our framework also gives new consistent surrogates and link functions which would likely have been extremely challenging to derive without our framework.

@@

%% also interesting to use Sec 4 to verify proposed canonical links
With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function.
Yet for some target problems, the search for consistent surrogates has been restricted to those accommodating a particular canonical link function, such as $k$ largest coordinates of the surrogate report in top-$k$ classification (\S~\ref{sec:top-k}).
Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$.
Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.
If the given $\psi$ is indeed consistent, then it is $\epsilon$-separated for sufficiently small $\epsilon$, so one can always construct such a $\Psi$ and verify that $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
See \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.

@@

Several authors consider a variant of multiclass classification, with the addition of an \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
For $\alpha \in (0,1)$, \citet{ramaswamy2018consistent} study the loss $\ell^\alpha : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^\alpha(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
\raft{Why do we have $\ell^\alpha$, $\psi^\alpha$ (superscripts) but $L_\alpha$ (subscript)?  Ideally we could make them uniform, but I wasn't sure what the considerations were}
\jessiet{No good reason, at the very least. I changed it.  \#burn}
%\begin{align}\label{eq:abstain-discrete}
%$\ellabs{\alpha}(r)_y = \begin{cases}
%0 & r = y\\
%\alpha & r = \bot\\
%1 & \text{otherwise}
%\end{cases}~.$
%\end{align}
The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. %: specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
For the case $\alpha=1/2$,
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L^{1/2}$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^{1/2}$ which are calibrated for $\ell^{1/2}$.
Letting $d = \ceil{\log_2(n)}$, their surrogate $L^{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L^{1/2}(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
\end{equation}
where $\varphi:[n]\to\{-1,1\}^d$ is an injection.%
\footnote{To translate our notation to that of \citet{ramaswamy2018consistent}, take $B = -\varphi$.}
% embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
Observe that $L^{1/2}$ is exactly hinge loss when $n=2$ and thus $d=1$. \jessiet{Remove this sentence?  or new paragraph below?}
The authors show that the link $\psi^{1/2}$ is calibrated\jessiet{IIRC, they actually show this a bit more generally.  basically, they show any $\epsilon$-separated link with $\| \cdot \|_\infty$ works.  Changing in text, but happy to revert.}, where
\begin{equation}\label{eq:abstain-link}
  \psi^{\epsilon}(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq \epsilon\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~,
\end{equation}
and they go on to establish linear surrogate regret bounds for $(L^{1/2},\psi^{1/2})$.

Using our framework, one can show that $L^{1/2}$ embeds (2 times) $\ell^{1/2}$, with the embedding given by $\varphi$ above where we define $\varphi(\bot) = 0 \in \reals^d$.
(Following the general procedure outlined above, the regions where $L^{1/2}$ is affine all have vertices in the set $\{-1,1\}^d \cup \{0\}$, meaning it is representative, and $L^{1/2}$ restricted to that set is precisely $2\ell^{1/2} \circ \varphi^{-1}$.)
%In light of our framework, we can see that $L^{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\epsilon}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
% and choosing $\psi^{1/2}(u) = \bot$ for all $u$ such that $\bot \in \Psi(u)$. 
%(For all $u$ such that $\bot \not \in \Psi(u)$, there is only one choice to link, e.g., $|\Psi(u)| = 1$.)
Hence, our framework could have simplified the process of finding $\psi^{1/2}$, and the corresponding proof of consistency and surrogate regret bounds.
% can be used to verify the calibration of the prposed link.
%\jessiet{changed this sentence.  Thoughts?}\raft{Changed it back, since I think our narrative here is that our framework would have simplified their paper}
To illustrate this point further, we give an alternate link $\psi'$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
\begin{equation}\label{eq:abstain-link-1}
  \psi'(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Construction~\ref{const:eps-thick-link} gives calibration of $(L^{1/2},\psi')$ with respect to $\ell^{1/2}$. 
%\jessiet{does it?  do we know $\epsilon$ is small enough for higher $d$?}\raft{removed ``immediately'' since you're right there are details to work out, but I'm pretty sure $\epsilon=1$ should hold for all $d$}
Aside from its simplicity, one possible advantage of $\psi'$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right? EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}\jessiet{is this last statement true just because $\epsilon$ is larger (and not because of norm choice?)?}.

@@

%% lovasz paper closes the gap, answering inconsistency wrt \ell^f by showing that L^f embeds structured abstain
\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular, and thus $\ell^f$ is a weighted Hamming loss.
Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.\jessiet{Changing $S$ to $A$ to not override notation from the submodular function.}
The inclusion of abstain options is natural when observing that the BEP surrogate $L^{1/2}$ from \S~\ref{sec:abstain} coincides with $L^f$ for the function $f(S) = \ones\{S \neq \emptyset\}$, so the multiclass abstain problem must be a special case of the Lov\'asz hinge.

@@

Actually determining this link function is nontrivial.
Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not always calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
Instead, they leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
Perhaps surprisingly, by deriving a link envelope $\Psi$ which is contained in the envelopes for $L^f$ for all submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
Thus, both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for all such $f$.

@@

\citet{wang2020weston} use the embedding framework to show that the Weston-Watkins hinge embeds the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
\raft{was citet*; what does that even do? \jessie{lists all authors (e.g., instead of Finocchiaro et al., goes to Finocchiaro, Frongillo, and Waggoner) \# burn}}
%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
%Let $T = \{T_1, \ldots, T_k\}$
The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
\begin{align*}
\T = \{ (T_0,\ldots,T_s) \mid s \geq 1, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_s = [n]\}~.
\end{align*}
\noindent
The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ embedded by Weston-Watkins hinge is then defined
\begin{align*}
\ell^\OP(T)_y &= \sum_{i=1}^{s} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
\end{align*}

@@

\raft{I am not sure what all Yutong and Scott show, but if the main point is restrictions on the conditional label distributions rendering the surrogate consistent, I'd say we should move this subsection ahead of top-$k$, and flesh out a bit more what exactly we mean by these restrictions and why we can conclude consistency under them (at a high level).  Then when we mention the same idea for top-$k$, we don't have to go into detail (and currently we don't). \jessie{they give some distributional constraints for $L^{WW}$ with the argmax link $\psi : u \mapsto \argmax_i u_i$ to be consistent w.r.t. 0-1 loss.}}
%% one might make distributional assumptions to regain consistency
Upon showing that $L^{WW}$ embeds $\ell^\OP$, \citeauthor{wang2020weston} proceed to use their characterization of $\prop{\ell^\OP}$ to give sufficient distributions assumptions over labels in $\P \subseteq \simplex$ such that $L^{WW}$ and the canonical argmax link $\psi^1(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).

%% how to understand level set simplex drawings
Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$.
Figure~\ref{fig:ordered-partition} gives the cells $\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$, outlined in solid black.
These cells are juxtaposed with the cells $\{p \in \simplex \mid y \in \mode(p)\}$ for each $y \in \Y$, outlined in dashed blue, for which $L^{WW}$ was originally proposed as a surrogate.
Since each distribution in a cell of $\prop{\ell^\OP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
Thus, if a cell of $\prop{\ell^\OP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ell^\OP}$ value can be mapped to the corresponding $\mode$ value.
Conversely, if the relative interior of a cell of $\prop{\ell^\OP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes these cells.
\jessiet{Next sentence redundant?  Can be massaged in to rest of paragraph?}
Fixing the canonical argmax link $\psi^1$ in Figure~\ref{fig:ordered-partition}, it suffices to make assumptions on the data distributions $\P$ excluding cells are depicted in blue in order to have calibration of $(L^{WW}, \psi^1)$ with respect to 0-1 loss on $\P$.
%\jessie{do we want more detail or save it for the caption?}
%\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1? \jessie{\#burn ?}}

\begin{figure}[H]
	\begin{minipage}{0.47\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\caption{Level sets of $\prop{\ell^\OP}$, the property elicited by the ordered partition loss and embedded by $L^{WW}$.
			The level sets of the mode (for which $L^{WW}$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
			The level sets of $\prop{\ell^\OP}$ whose relative interiors span multiple cells of the mode cannot be properly linked to the mode.
			Here, this is demonstrated as the report corresponding to the cell has highest partition has more than one element, where in the white cells, the ``highest'' element of the partition is well-defined.}
		\label{fig:ordered-partition}
	\end{minipage}
\end{figure}

\subsection{Surrogates for top-$k$ classification}
\label{sec:top-k}
% In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and upon realizing outcome $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
% Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
% Satisfying all three desiderata simultaneously had not been observed until the work of~\citet{finocchiaro2022consistenttopk}.\raft{Not sure you can use ``observed'' like that (came up a few times)}
% The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$.
% \citet{lapin2016loss} observes that this approach learns more information than desired and often requires more samples
% % for surrogate regret to approach target regret
% ~\citep{frongillo2021surrogate}.\jessiet{right?}
% \citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
% Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of $k$ labels, and given the true label $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
In the literature on surrogates for top-$k$ classification, one goal has been to find a surrogate satisfying the following three desiderata: convexity, consistency, and piecewise linear (``hinge-like'') structure.
\citet{yang2018consistency} show that a number of previously proposed polyhedral losses, i.e., those which are convex and hinge-like, are inconsistent.
They further suggest that perhaps no surrogate could satisfy all three properties.
%\raft{Not sure you can use ``observed'' like that (came up a few times; see original)}
\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do \jessie{makes sense! \#burn}}

>>>>

%% overview of the applications
Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete target loss, as well as to verify consistency or inconsistency for specific surrogate and link pairs.
Below, we illustrate the power of this framework with specific examples from the literature.
To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, which is an embedding, and show how to rederive their link function and surrogate regret bounds (\S~\ref{sec:abstain}). 
We then give three examples of subsequent works that use our framework, in the context of structured binary classification (\S~\ref{sec:lovasz-hinge}), multiclass classification (\S~\ref{sec:winge}), and top-$k$ classification (\S~\ref{sec:top-k}).
In all cases, our framework illuminates the behavior of inconsistent surrogates by revealing the discrete losses they embed, i.e., the true targets for which they are consistent.
In structured binary classification and top-$k$ classification, our framework also gives new consistent surrogates and link functions which would likely have been extremely challenging to derive without our framework. \jessiet{Want to be careful on this claim and make sure it doesn't sound like we do both surrogate and link for both.}

@@

%% also interesting to use Sec 4 to verify proposed canonical links
With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function.
Yet for some target problems, the search for consistent surrogates has been restricted to those accommodating a particular canonical link function, such as $k$ largest coordinates of the surrogate report in top-$k$ classification (\S~\ref{sec:top-k}).
Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$. \jessiet{Redundant from \S 4 but I think that's okay.  I like it in both spots}
Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.
If the given $\psi$ is indeed consistent, then it is $\epsilon$-separated for sufficiently small $\epsilon$, so one can always construct such a $\Psi$ and verify that $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
See \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.

@@

Several authors consider a variant of multiclass classification, with the addition of an \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
For $\alpha \in (0,1)$, \citet{ramaswamy2018consistent} study the loss $\ell^\alpha : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^\alpha(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
%\raft{Why do we have $\ell^\alpha$, $\psi^\alpha$ (superscripts) but $L_\alpha$ (subscript)?  Ideally we could make them uniform, but I wasn't sure what the considerations were}
%\jessiet{No good reason, at the very least. I changed it.  \#burn}
%\begin{align}\label{eq:abstain-discrete}
%$\ellabs{\alpha}(r)_y = \begin{cases}
%0 & r = y\\
%\alpha & r = \bot\\
%1 & \text{otherwise}
%\end{cases}~.$
%\end{align}
The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. %: specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
For the case $\alpha=1/2$,
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L^{1/2}$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^{1/2}$ which are calibrated for $\ell^{1/2}$.
Letting $d = \ceil{\log_2(n)}$, their surrogate $L^{1/2} : \reals^d \to \reals^\Y_+$ is given by
\begin{equation}\label{eq:abstain-surrogate}
L^{1/2}(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
\end{equation}
where $\varphi:[n]\to\{-1,1\}^d$ is an injection.%
\footnote{To translate our notation to that of \citet{ramaswamy2018consistent}, take $B = -\varphi$.}
% embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
Observe that $L^{1/2}$ is exactly hinge loss when $n=2$ and thus $d=1$. \jessiet{Remove this sentence?  or new paragraph below?}
The authors show that the link $\psi^{1/2}$ is calibrated\jessiet{IIRC, they actually show this a bit more generally.  basically, they show any $\epsilon$-separated link with $\| \cdot \|_\infty$ works.  Changing in text, but happy to revert.}, where
\begin{equation}\label{eq:abstain-link}
  \psi^{\epsilon}(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq \epsilon\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~,
\end{equation}
and they go on to establish linear surrogate regret bounds for $(L^{1/2},\psi^{1/2})$.

Using our framework, one can show that $L^{1/2}$ embeds (2 times) $\ell^{1/2}$, with the embedding given by $\varphi$ above where we define $\varphi(\bot) = 0 \in \reals^d$.
(Following the general procedure outlined above, the regions where $L^{1/2}$ is affine all have vertices in the set $\{-1,1\}^d \cup \{0\}$, meaning it is representative, and $L^{1/2}$ restricted to that set is precisely $2\ell^{1/2} \circ \varphi^{-1}$.)
%In light of our framework, we can see that $L^{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\epsilon}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
% and choosing $\psi^{1/2}(u) = \bot$ for all $u$ such that $\bot \in \Psi(u)$. 
%(For all $u$ such that $\bot \not \in \Psi(u)$, there is only one choice to link, e.g., $|\Psi(u)| = 1$.)
Hence, our framework could have simplified the process of finding $\psi^{1/2}$, and the corresponding proof of consistency and surrogate regret bounds.
% can be used to verify the calibration of the prposed link.
%\jessiet{changed this sentence.  Thoughts?}\raft{Changed it back, since I think our narrative here is that our framework would have simplified their paper}
To illustrate this point further, we give an alternate link $\psi^1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
\begin{equation}\label{eq:abstain-link-1}
  \psi^1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Construction~\ref{const:eps-thick-link} gives calibration of $(L^{1/2},\psi^1)$ with respect to $\ell^{1/2}$. 
%\jessiet{does it?  do we know $\epsilon$ is small enough for higher $d$?}\raft{removed ``immediately'' since you're right there are details to work out, but I'm pretty sure $\epsilon=1$ should hold for all $d$}
Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right? EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}\jessiet{is this last statement true just because $\epsilon$ is larger (and not because of norm choice?)?}.

@@

%% lovasz paper closes the gap, answering inconsistency wrt \ell^f by showing that L^f embeds structured abstain
\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular, and thus $\ell^f$ is a weighted Hamming loss.
Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.\jessiet{Changing $S$ to $A$ to not override notation from the submodular function.}
The inclusion of abstain options is natural when observing that the BEP surrogate $L^{1/2}$ from \S~\ref{sec:abstain} coincides with $L^f$ for the function $f(S) = \ones\{S \neq \emptyset\}$, so the multiclass abstain problem is a special case of the Lov\'asz hinge.

@@

Actually determining this link function is nontrivial.
Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not always calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
Instead, they leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
Perhaps surprisingly, by deriving the link envelope $\Psi$ which is contained in the envelopes for $L^f$ for all submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
Thus, both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for all such $f$.

@@

\citet{wang2020weston} use the embedding framework to show that the Weston--Watkins hinge embeds the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
%Let $T = \{T_1, \ldots, T_k\}$
The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
\begin{align*}
\T = \{ (T_0,\ldots,T_s) \mid s \geq 1, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_s = [n]\}~.
\end{align*}
\noindent
The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ embedded by Weston-Watkins hinge is then defined
\begin{align*}
\ell^\OP(T)_y &= \sum_{i=1}^{s} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
\end{align*}

@@

\raft{I am not sure what all Yutong and Scott show, but if the main point is restrictions on the conditional label distributions rendering the surrogate consistent, I'd say we should move this subsection ahead of top-$k$, and flesh out a bit more what exactly we mean by these restrictions and why we can conclude consistency under them (at a high level).  Then when we mention the same idea for top-$k$, we don't have to go into detail (and currently we don't). \jessie{they give some distributional constraints for $L^{WW}$ with the argmax link $\psi : u \mapsto \argmax_i u_i$ to be consistent w.r.t. 0-1 loss.}}
%% one might make distributional assumptions to regain consistency
Upon showing that $L^{WW}$ embeds $\ell^\OP$, \citeauthor{wang2020weston} proceed to characterize $\prop{\ell^\OP}$ and use it to give sufficient distributions assumptions over labels in $\P \subseteq \simplex$ such that $L^{WW}$ and the canonical argmax link $\psi^1(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).

%% how to understand level set simplex drawings
Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
Figure~\ref{fig:ordered-partition} gives the cells $\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$, outlined in solid black.
These cells are juxtaposed with the cells $\{p \in \simplex \mid y \in \mode(p)\}$ for each $y \in \Y$, outlined in dashed blue, for which $L^{WW}$ was originally proposed as a surrogate.
Since each distribution in a cell of $\prop{\ell^\OP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
Thus, if a cell of $\prop{\ell^\OP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ell^\OP}$ value can be mapped to the corresponding $\mode$ value.
Conversely, if the relative interior of a cell of $\prop{\ell^\OP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes these cells, colored in blue in Figure~\ref{fig:ordered-partition}.
\jessiet{Commented out next sentence for redundancy - May 3, 22}
%Fixing the canonical argmax link $\psi^1$ in Figure~\ref{fig:ordered-partition}, it suffices to make assumptions on the data distributions $\P$ excluding cells are depicted in blue in order to have calibration of $(L^{WW}, \psi^1)$ with respect to 0-1 loss on $\P$.

\begin{figure}[H]
	\begin{minipage}{0.47\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\caption{Level sets of $\prop{\ell^\OP}$ (solid lines)
			%the property elicited by the ordered partition loss and embedded by $L^{WW}$, 
			juxtaposed against the level sets of $\mode$ (dashed lines).
%		The level sets of the mode (for which $L^{WW}$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
		The level sets of $\prop{\ell^\OP}$ whose relative interiors span multiple cells of the mode cannot be properly linked to the mode.
		Here, this is demonstrated as the report corresponding to the cell has highest partition has more than one element, where in the white cells, the ``highest'' element of the partition is well-defined.}
		\label{fig:ordered-partition}
	\end{minipage}
\end{figure}

\subsection{Surrogates for top-$k$ classification}
\label{sec:top-k}
% In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and upon realizing outcome $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
% Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
% Satisfying all three desiderata simultaneously had not been observed until the work of~\citet{finocchiaro2022consistenttopk}.\raft{Not sure you can use ``observed'' like that (came up a few times)}
% The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$.
% \citet{lapin2016loss} observes that this approach learns more information than desired and often requires more samples
% % for surrogate regret to approach target regret
% ~\citep{frongillo2021surrogate}.\jessiet{right?}
% \citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
% Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of $k$ labels, and given the true label $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
In the literature on surrogates for top-$k$ classification, one goal has been to find a surrogate satisfying the following three desiderata: convexity, consistency, and piecewise linear (``hinge-like'') structure.
\citet{yang2018consistency} show that a number of previously proposed polyhedral losses, i.e., those which are convex and hinge-like, are inconsistent.
They further suggest that perhaps no surrogate could satisfy all three properties.
%\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do \jessie{makes sense! \#burn}}
